### 2019-02-18 manuscript/introduction.tex
- I took over the start of the Intro for my part - (it's right at the top, so you can't miss it) - this is a backup, TBC tomorrow morning (2/18/2019)

\section{Introduction}
-Studying diversification linked to trait evolution\newline
Here I need help (perhaps will be the last line I write)\newline
In these context, botanist have been asking how polyploidy shapes patterns of diversification. The prevalence of polyploidy and its detection across multiple and highly diverse clades of angiosperms inevitably lead to the hypothesis of the importance of polyploidy in the speciation and extinction patterns observed across the flowering plant phylogeny. At the same time, a similar question has been asked in the breeding system world, where self-compatibility has evolved multiple times in flowering plants. However, the influence in diversification using both polyploidy and self-compatibility information has not been studied simultaneously.

@@

- What is lacking from past approaches? \newline
There are two key questions that at the time of the polyploidy debate were difficult to ask. The first is if the models used to measure the diversification of polyploids were correct, and the second question is if the models have potentially included more evidence and potential traits that are not polyploidy or other lines of evidence that could be driving the patterns. At the time, in a different context \citet{beaulieu_2016} were finding an alternative solution to the first question, coming up with a new model that could represent the broad heterogeneity of the diversification process and parse out the signal between the trait of interest and the noise in diversification. Their model, the hidden state speciation and extinction model is a key component to detect whether polyploidy our something else unknown but related to it is driving the speciation and extinction patterns that we see in angiosperms. \newline

-What is our proposal to tackle this problem?\newline

- How this paper is structured \newline

@@

=

>>>>

\section{Introduction}

% Outline, discussed by Boris and Emma:
%
% we are interested in the evolution of traits and their influence on lineage diversification
%     ref Barrett work 
% 		no diversification?, but trait shifts:
%		barrett_1996 (mating system + LH)
%		barrett_2013
%		barrett_2008: "Because polyploidy affects the entire genome, it is perhaps not surprising that it influences many as- pects of the phenotype, including the mating system. However, although it has long been recognized that the evolutionary tran sition from diploidy to polyploidy may result in correlated changes in mating patterns, the theoretical and empirical evidence is limited and often contradictory." (p.5)
%
%     any one study focuses on one/few traits
%     but any real organisms have many, so need to enlarge our view
%     mini "here, we..."
% we have tools to try to answer these questions
%     sse models
%     issues
%     but a way forward is to allow for multiple factors that could influence diversification
% ploidy
%     Stebbins
%     Mayrose, Soltis
%     recent paleo WGD, diploidization
% breeding system
%     directionality
%     diversification in Solanaceae
%     correlation with ploidy
%     pathways from SI-D to SC-P: direct or via SC-D
% here, we...
%     diversification: interaction between ploidy and breeding system
%     also: diploidization, pathways

%B: I placed this out of order, so you can see it
The prevalence and significance of polyploidy was broadly considered a salient feature of flowering plants \citep{}, even before the advent of genomic tools dramatically escalated the stakes, so that nearly flowering plants are thought to have undergone at least one round of polyploidization \citep{}.
It is therefore perhaps surprising that there appears to be little agreement regarding the evolutionary consequences of polyploidy, especially how it affects diversification rates. %species richness.
% I think Rosana wants this part here (above)
% next, continue with ploidy narrative (mayrose/soltis)

Polyploidization changes the genomic content of all cells, and consequently has the potential to affect a wide variety, if not all traits. 
Among the many of changes associated with polyploidization, perhaps the most prominent is the association between polyploidy and propensity for self-fertilization \citep{stebbins_1950, grant_1956, barrett_1988}.
Polyploidization is not only suspected of a mere correlated change in breeding systems, but of a causal link.
By disrupting certain genetic self-incompatibility systems, polyploidy is also associated with the ability to self-fertilize in many plant groups (Miller and Venable, 2000; Mable, 2004; Robertson et al., 2011).
% It's not Spencer's best line, but it's not bad for our work: Barrett 2008: Because polyploidy affects the entire genome, it is perhaps not surprising that it influences many aspects of the phenotype, including the mating system. However, although it has long been recognized that the evolutionary transition from diploidy to polyploidy may result in correlated changes in mating patterns, the theoretical and empirical evidence is limited and often contradictory. 
%
% how polyploidy breaks down SI
% how that generates associations (and variable associations of mating system and ploidy! husband2008, others cited by barrett_2013

% Breeding systems also affect diversification rate and so there could be an interaction
% we also have this great data for SI loci and the transition could be even more common, providing power to resolve the great diversification questions
% set up pathways

Studying diversification linked to trait evolution\newline
% Here I need help (perhaps will be the last line I write)
%In these context, botanist have been asking how polyploidy shapes patterns of diversification. 
The prevalence of polyploidy and its detection across multiple and highly diverse clades of angiosperms inevitably lead to the hypothesis of the importance of polyploidy in the speciation and extinction patterns observed across the flowering plant phylogeny. 
At the same time, a similar question has been asked in the breeding system world, where self-compatibility has evolved multiple times in flowering plants. 
However, the influence in diversification using both polyploidy and self-compatibility information has not been studied simultaneously.

@@

- What is lacking from past approaches? \newline
There are two key questions that at the time of the polyploidy debate were difficult to ask. The first is if the models used to measure the diversification of polyploids were correct, and the second question is if the models have potentially included more evidence and potential traits that are not polyploidy or other lines of evidence that could be driving the patterns. At the time, in a different context \citet{beaulieu_2016} were finding an alternative solution to the first question, coming up with a new model that could represent the broad heterogeneity of the diversification process and parse out the signal between the trait of interest and the noise in diversification. Their model, the hidden state speciation and extinction model is a key component to detect whether polyploidy our something else unknown but related to it is driving the speciation and extinction patterns that we see in angiosperms. \newline
What is our proposal to tackle this problem?\newline

@@
